\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits. 



The amount of blood in the human body can depend on a few factors, like your sex, how much you weigh, and even where you live, but generally equivalent to 7\% of the body weight. The amount of blood in the human body differs based on where you live. For example, people who live at higher altitudes usually have more blood because there isn’t as much oxygen at lower altitudes. The main component of the blood is plasma, which takes up 55\% of it.
The plasma allows the blood to flow freely throughout the entire body inside blood vessels. Based on different attributes of the blood’s cellular components, like colour, size, texture, composition and shape, they are separated into three cell types: erythrocytes also known as Red Blood Cells (RBC), leukocytes (White Blood Cells) and thrombocytes. Observing these molecules under the microscope, they have distinct shapes and sizes, WBCs being the larger ones due to the presence of nuclei and cytoplasm inside them. 
Based on these features WBC are further divided into two types: granulocytes and agranulocytes. 
Granulocytes are the most common WBC types defined by the granules inside their cytoplasm. The granulocytes, if dyed, can be categorized into four subtypes. These types differ in the colour of the granule stains inside the cytoplasm. The four cell types are neutrophils, eosinophils, basophils, and mast cells. The other type of WBC are agranulocytes that don't have granules in their cytoplasm and are further categorized into lymphocytes and monocytes.

%figure about WBC cells

A sample of 1 µl of human blood sample contains between 4000 and 11000 WBC. The distribution of different WBC types are the followings: neutrophils between 40\% and 70\%, lymphocytes between 20\% and 45\%, monocytes between 2\% and 10\%, eosinophils between 1\% and 6\% and basophils under 1\%. Although basophils make up less than 1\% of the blood, they play an important role in the health of humans. Any minor imbalance can cause serious health issues, e.g., leukemia, 
% https://www.sciencedirect.com/science/article/pii/S0169260718317802?via%3Dihub
which has been considered as the leading death cause among various cancers due to lack of proper treatment. So it is important to diagnose the disease in the early stage. To avoid these kinds of diseases, it is necessary to determine the distribution and the exact count of WBC in the body. At the present there are two commonly used ways to achieve this: the first method involves a specialist who manually counts the cells with the help of a hemocytometer, while the other method is using an automated analyzer.
%https://mural.uv.es/basgaros/Cell-counting-Neubauer-chamber.pdf
%https://www.sciencedirect.com/science/article/pii/B978012427150050098X?via%3Dihub

Complete blood count
%https://www.sciencedirect.com/science/article/pii/S0956566319310139?via%3Dihub
is a blood analyzer which allows one to determine the count of the blood cells present in the body. This allows the diagnosis of various disorders, for example, a lower WBC count than normal, called leukopenia, can forecast the presence of marrow cancer, autoimmune diseases, thyroid disorder, etc. A higher WBC count than normal can be a sign of a foreign substance present in the body. This is called leukocytosis and can cause several serious diseases like leukemia, marrow malformation, etc. In the treatment of these disorders, the key aspect is early diagnosis. In the treatment of leukemia early diagnosis greatly increases the chance of recovery, especially in children.

To achieve an early diagnosis, efficient and fast techniques are necessary so that the count and state of WBC can be determined to conclude results. 
